\plaintitle

### 2021-01-31 draft.tex
Finished the paper

% Copyright
\CopyrightYear{2021}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
\doi{https://doi.org/10.1145/3313831.XXXXXXX}
% ISBN
\isbn{XXX-X-XXXX-XXXX-X/21/05}
%Conference
\conferenceinfo{CHI'21,}{May 8--13, 2021, Yokohama, Japan}
%Price
%\acmPrice{\$15.00}

@@

% Arabic page numbers for submission.  Remove this line to eliminate
% page numbers for the camera ready copy
% \pagenumbering{arabic}

@@

@@

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
\usepackage{todonotes}

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Lifestyle and study equipment changes during distance learning}
\def\plainauthor{First Author, Second Author, Third Author,
  Fourth Author, Fifth Author, Sixth Author}
\def\emptyauthor{}
\def\plainkeywords{distance learning; student; home office; study environment; work environment; motivation; pandemic; health; }
\def\plaingeneralterms{Documentation, Standardization}

@@

% End of preamble. Here it comes the document.
\begin{document}
\title{\plaintitle}
\numberofauthors{4}
\author{
  \alignauthor{Author One\\
    \affaddr{for Submission}\\
    \affaddr{}\\
    \email{}}\\
  \alignauthor{Author Two\\
    \affaddr{for Submission}\\
    \affaddr{}\\
    \email{}}\\
  \alignauthor{Author Three\\
    \affaddr{for Submission}\\
    \affaddr{}\\
    \email{}}\\
  \alignauthor{Author Four\\
    \affaddr{for Submission}\\
    \affaddr{}\\
    \email{}}\\
}
\maketitle
\begin{abstract}
Given the appearance of the new pathological risk incurred during the 2020 Covid-19 pandemic, most educational institutions, be them either lower or higher educational, have had to restrict their activity on-campus and promote a fully online pedagogical methodology in order to avoid the spread of the virus and protect the health of both students and teachers. By employing already existing software solutions to the likes of \emph{Zoom}, \emph{Microsoft Teams}, and other existing tools, courses have been completely moved within the realm of the internet to the best of the ability of each educational institution. In this context, the authors are trying to investigate the effects that the sudden move to distance learning has had on students from different backgrounds, as well as how they have been forced to change their study and work environment to cope with the perpetual stress of academic life within the confines of their own home.
\end{abstract}

% ACM Classfication

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003456.10003457.10003527.10003542</concept_id>
<concept_desc>Social and professional topics~Adult education</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121</concept_id>
<concept_desc>Human-centered computing~Human computer interaction (HCI)</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10003122.10003334</concept_id>
<concept_desc>Human-centered computing~User studies</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

At the start of 2020, most countries around the world have had to impose strict restriction upon public spaces and institution in order to combat the eventual spread of Covid-19 within their populations. One measure imposed upon the educational systems was to forbid as much as possible lectures and other educational activities within their campuses as to avoid unnecessary and possible life-threatening contact between members of the institutions. In order to continue with the already started semester, most if not all education institutions have put forward online procedures based on already existing infrastructure in order for courses to still take place. Students have suddenly found themselves studying full time from the comfort of their home, not needing to travel to the universities campuses anymore. During their own experiences as students within the Summer 2020 semester, the authors have notice certain trends within their own behaviour and that of fellow students related to the unpreparedness of their own home-study environment and the rising motivational issues, and so, decided to perform an inquiry under the course work for the User Research Methods PR at the Technical University of Vienna, in order to investigate if indeed there was a general unpreparedness across the student population for such a drastic move to distance learning, as well as, if there is such a notion as a \emph{perfect study environment}, and in the end, conclude with a small \emph{tips and tricks} handbook which other students might find helpful in order to increase their comfort and motivation for studying at home and eventually decrease the amount of stress cause by social isolation.\cite{fauci_lane_redfield_2020, hossain_mental_2020}

@@

Here we should probably talk about the previous papers we read about distance learning, social isolation, education during other pandemics, as well as papers about the research methodologies.

@@

\subsubsection{Research Questions}

\subsection{Methodologies}
In order to perform their research as best as possible, the authors have decided on utilizing three separate methodologies in order to achieve a coherent approach and take into account as many aspects related towards \emph{study environments} as possible. They started by performing auto-ethnography upon themselves to have an introspective look over their own experience during the first and second semesters of their studies within the context of the pandemic restrictions. Using the findings of the auto-ethnography, they have arrived at a number of interview questions that where used in a series of semi-structured interviews with participants outside of the research team. Ending by performing an photographic ethnography of pictures taken by the same interview participants in order to analyse them in parallel with the interview transcriptions and achieve a more coherent image of each participants actual study environments.

@@

Before starting the auto-ethnography research, each researcher has been given an information sheet and consent form which had to be sign by the research-participant and one of the other researchers. The structure of the document has been agreed upon unanimously by the team as so to avoid any potential issues related to data privacy of the resulting documents from the auto-ethnographic research.

After signing the consent form, each researcher has had to conduct an inner-inquiry upon his or hers experience that resulted from the drastic change towards full-time studying from home, as well as making a comparison between their study/work environment and study workload between their previous semester (e.g. Winter 2019/2020) and the next restricted semesters (e.g. Summer 2020, Winter 2020/2021).

Upon finishing their report about their own experience, each researcher had to take a picture of their current study environment/s (see Figure~\ref{fig:figure1} as an example) and attach it to the report. Afterwards all reports where analysed by each researcher, and researcher-participant had to perform a presentation of their experience to all other researchers. Findings culminating in organizing the information using thematic analysis using Miro\footnote{\url{https://miro.com/}} and extracting possible interview questions for their findings. After having decided on the possible interview questions, sample semi-structured interview took place, having one of the researchers as a participant, and two others as interviewer and observer. Upon finishing the sample interview, the interview question had been filtered to only five central questions as so to provide a structure for the incoming participant interviews.
\begin{figure}
\centering
  \includegraphics[width=0.9\columnwidth]{figures/auto-e-picture}
  \caption{Sample picture from the Auto-Ethnographic method, showing the desk of one of the researchers}~\label{fig:figure1}
\end{figure}

\subsubsection{Semi-structured Interviews}
The 5 interview questions
Who were the participants (general information), where the interviews were taken, how we found the participants, age, academic status, consent management, tools, analysing the interview, miro idea board / extracting data THEMATIC ANALYSING

Some people did not know how the pandemic will evolve so they did not prepare for a long home learning situation, we asked them how the ideal setup will look like or if they know the next semesters  will be remotely what will they change.

issues: Single interviewer, no observer., subjectivity issues due to the participants being friends

\subsubsection{Photographic Ethnography}
Using the photo analysis method, the researches wanted to discover the study setups of students engaged in distance learning. The method was chose to give a better overview of essential items used by students for improving the health and comfort during online studies, at home. The participants agreed on sending a photo of their environment before the semi-structured online interviews. Moreover, the researchers shared photos of their personal setups used for remote studies. Two consents were used in the research: one sent to the participants before the semi-structured online interview, and another, for the researchers themselves, before starting the auto-ethnography process. The processes of storing, analyzing, anonymizing and deletion of the participants and researchers photos were covered in the mentioned consents.

As visual recording of the personal space …, not all the participants agreed to expose their working space. A number of X photos was collected in the photo analysis process. A visual difference between the state of the learning environment before and after switching to distance learning could not been made, as the photos received by the researchers were taken in the actual context of the pandemic. Only one participant sent photos of their old and their actual setup.  One participant sent a photo of their current setup, and two photos of setups that could serve as inspiration for their ideal setup. All photos received by the participants were used in the analyze process.

\begin{figure}
\centering
  \includegraphics[width=0.9\columnwidth]{figures/perfect-setup}
  \caption{A sample photo from the Photographic Ethnography method given by one of the participants, it is the desired "perfect study environment''}~\label{fig:figure1}
\end{figure}

@@

We need to talk about the research question results here.

Our findings from the interviews

Our findings from the photos: Both participants and from the auto-ethnography

The analyze of the photos received from the participants and from the researchers involved in the study, showed unique, personalized study environments,  with a commune focus on ergonomics, efficiency and aesthetics. The result showed that the position of the working desk is usually located close to a direct source of natural light.  The importance of a natural source of light was mentioned by several participants during the semi-structured online interview process. Items such as: second screen, laptop, lamp, plants, notebooks were …

@@

Things to talk about: 
1.Universities could open libraries or study spaces. Even increase the amount of space post-pandemic, as an issue already existed
2. Items that are we recommend to use for study and the uni should give discounts to
3.

\subsection{Limitations}

\section{Implications for design}

It is worth noting that the research presented within this paper is not meant necessarily to provide the HCI community with a new form of interaction or a profoundly new methodological approach in how human-computer interaction can be studied, but it is meant to be seen more through the lens of \cite{dourish_implications_2006} where the significance of \emph{``Implications for design''} stems from observing human habits within a highly isolated scenario where most of the study and work interactions are perpetuated solely through technology. The authors desire is not to emphasize the need for bigger screens, or more comfortable chairs, but to show how much of our lives \emph{can} be replaced through software.

\subsection{Office of the next pandemic}

Given our interviews with the participants, no clear generalizing statement can be drawn on previous study setups possessed before the enactment of social distancing norms. But several have attributed a more aware understanding of the need to have such an environment within their homes. 
Noticing the likely-hood of our current situation to continue for at least one more semester, multiple participants had come to the conclusion and indeed already have plans of improving their study and work environments. Putting in question if a need in providing highly economical solutions in so as to reduce the overall cost of creating such a setup might be the next and most valuable step for the industry to take.

\subsection{Replacement of social interaction}

Multiple participants have expressed an inner desired to talk about their motivational issues while studying in this new environment. And to our amazement, different solutions in coping have been applied by each, from simple \emph{Zoom} study meetups, to arguably illegal (though depending on the country, might not be) face-to-face lecture viewings. Here the authors would like to express that a proper replacement of the in-class lecture experience, still does not exist and some participants have even emphasized a small regress due to the constant gap in interactivity that distance learning cannot overcome.

\section{Conclusions and future work}

1. A study on a more diverse group of students
2. A more in-depth study about motivational aspects
3. West country rich 
4. Didn’t realize the length of the pandemic
5. What could the regulations look like?
6. Maybe (?) we have a OK demographic picture of the participants (students)

\section{Acknowledgments}
Thank you to all our interview participants for taking their time off their studies and work in order to help us with this assignment. Thank you to TU Wien for giving us access to the needed tools in order to prepare the assignment,  \textit{as good as they are}. No other funding was provided.

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{sample}

>>>>

% Copyright
\CopyrightYear{2021}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
\doi{https://doi.org/10.1145/3313831.XXXXXXX}
% ISBN
\isbn{XXX-X-XXXX-XXXX-X/21/05}
%Conference
\conferenceinfo{CHI'21,}{May 8--13, 2021, Yokohama, Japan}
%Price
%\acmPrice{\$99.90}

@@

% Arabic page numbers for submission.  Remove this line to eliminate
% page numbers for the camera ready copy
\pagenumbering{arabic}

@@

\usepackage{comment} %OSCARs insert

@@

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
% \usepackage{todonotes}

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{The Pandemic Home Office For University Studies}
\def\plainauthor{First Author, Second Author, Third Author, Fourth Author}
\def\emptyauthor{First Author, Second Author, Third Author, Fourth Author}
\def\plainkeywords{distance learning; health; home office; motivation; pandemic; student;  study environment; work environment;}
\def\plaingeneralterms{Documentation, Standardization}

@@

% End of preamble. Here it comes the document.
\begin{document}
\title{\plaintitle}
\numberofauthors{4}

\author{
    Andreea-Valentina Roman\\
    \affaddr{Vienna University of Technology}\\
    \affaddr{Vienna, Austria}\\
    \email{e12019805@student.tuwien.ac.at}
    \and
  Dragos-Alexandru Gabor\\
    \affaddr{Vienna University of Technology}\\
    \affaddr{Vienna, Austria}\\
    \email{e11932446@student.tuwien.ac.at
}
 \and
Joanna Zamiechowska\\
    \affaddr{Vienna University of Technology}\\
    \affaddr{Vienna, Austria}\\
    \email{e11936038@student.tuwien.ac.at}
 \and
Oscar Larsson\\
    \affaddr{Vienna University of Technology}\\
    \affaddr{Vienna, Austria}\\
    \email{e12015240@student.tuwien.ac.at}

}

\begin{comment}
\author{
  Andreea Roman\\
  \affaddr{Vienna University of Technology}\\
    \affaddr{Vienna, Austria}\\
    \email{e12019805@student.tuwien.ac.at}
  \and
  Dragos-Alexandru Gabor\\
  \affaddr{Vienna University of Technology}\\
    \affaddr{Vienna, Austria}\\
    \email{e12019805@student.tuwien.ac.at}
    \AND
  Dragos-Alexandru Gabor\\
  \affaddr{Vienna University of Technology}\\
    \affaddr{Vienna, Austria}\\
    \email{e12019805@student.tuwien.ac.at}
    \and
  Dragos-Alexandru Gabor\\
  \affaddr{Vienna University of Technology}\\
    \affaddr{Vienna, Austria}\\
    \email{e12019805@student.tuwien.ac.at}
}
\end{comment}

\maketitle

\begin{abstract}
Given the appearance of the new pathological risk incurred during the COVID-19 pandemic, most educational institutions, be they either lower or higher education, have had to restrict their on-campus activities and promote a fully online pedagogical approach in order to avoid the spread of the virus and protect the health of both students and teachers. By employing already existing software solutions facilitating video streaming (e.g. Zoom) and course management (e.g. Moodle), courses have, in most cases, been completely moved into the realm of the internet to the best of the ability of each educational institution. In this context, we are trying to investigate the effects that the sudden move to distance learning has had on students of different backgrounds, as well as how they have been forced to change their study and work environments to cope with the perpetual stress of academic life within the confines of their own home. After analyzing eight different student situations, there are indications that many students have a lower level of motivation in the current distance learning format. The technical equipment is upgraded but not always fully complete. There is still a majority who are not satisfied with their home office furnishings, mainly the office chair. However, there seems to be a lack of awareness of how simple ergonomics can be improved, partly because the student has downgraded this priority in the hope of soon returning to normal campus studies. Financial limitations are also a constraint.
\end{abstract}

%Not to use, repetitive: The equipment varies depending on the student and situation.

% ACM Classfication
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003456.10003457.10003527.10003542</concept_id>
<concept_desc>Social and professional topics~Adult education</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121</concept_id>
<concept_desc>Human-centered computing~Human computer interaction (HCI)</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10003122.10003334</concept_id>
<concept_desc>Human-centered computing~User studies</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

At the start of 2020, most countries around the world have had to impose strict restrictions upon public spaces and institutions in order to combat the eventual spread of COVID-19 within their population. One measure imposed upon the educational system was to forbid as much as possible lectures and other educational activities within their campuses as to avoid unnecessary and possibly life-threatening contact between students and members of the institution. In order to continue with the already started semester, most if not all education institutions have put forward online procedures based on existing infrastructure in order for the courses to still take place. Consequently, students have suddenly found themselves studying full-time from their homes, no longer allowed to study in libraries, cafes, or at the university campus. \\

Not being able to study on campus as a student can be frustrating as well as challenging. A study from 2002 showed that "e-learning" was so challenging that approximately 80\% of those who participated in such a course would fail \cite{1}. Today, almost 20 years later, the circumstances have changed. Over the past 20 years, technology has developed radically and have improved conditions for how distance-based studies can be conducted. Since the turn of the millennium higher education institutions have had the opportunity to expand large parts of their functions with digital solutions \cite{2}. Offering distance learning not only improves students' study conditions but also allows better opportunities for the university to remain international, future-oriented, and profit-driven \cite{2}. For example, a university that offers distance learning attracts more students from other locations, nationally as well as internationally. Digital solutions in terms of online procedures and digital learning platforms are fundamental to the university's modern infrastructure, although this internal infrastructure has not previously been tested for a complete shift to distance learning during a pandemic. \\

We, the research team of this conference paper, have also noticed certain trends of our own study behaviour during the distance learning semesters in Summer 2020 and Winter 2020. We have become aware of rising motivational issues due to distance learning. However, there is still an uncertainty as to whether this is true for the majority of the student population, and how unique situations may affect home learning. Hence, the following conference paper will perform an inquiry under a practice research study for the course \textit{193.056 User Research Methods Project} at Vienna University of Technology, Austria, in order to investigate this issue. The research study will examine if there is a general unpreparedness across the student population for such a drastic move to distance learning, as well as if there is such a notion as a \emph{``perfect study environment or study setup''}. This research result will help us compile recommendations for both students and educational institutions, which aim to help reduce the amount of stress caused by social isolation and full-time distance learning, and increase students' acceptance of the distance learning situation \cite{fauci_lane_redfield_2020, hossain_mental_2020}.

%HCI, do we need more of this in this paper?

@@

The following paper is related to a British motivation research study that examined the basic factors that influence successful distance learning \cite{simons_leverett_beaumont_2019}. The research established how the students' knowledge and autonomy relate to the inherent motivation in a distance-adapted study environment, and how the educational institution may affects this result. It should be added that this research was conducted before the COVID-19 pandemic and therefore describes a distance learning situation that differs from the current situation. However, the research identifies various factors that affect the students' results in a distance learning setting. We believe that continuously supporting the student is a fundamental factor for a successful outcome. This applies not only for universities but also for family, friends, and employers. Feedback needs to be adapted to each student. Communication should take place with one-to-one contact. Supporting the student means that the student is more likely to make conscious choices in their studies. Another important aspect is flexibility and the need to be able to adapt the studies depending on the students' needs. For example, accessing study materials online can be a form of flexibility. Consequently, intrinsic motivation consists of an interplay between support and flexibility, which should be taken into account when investigating this topic.

Preceding all research methodologies, we conducted other literature reviews related to distance learning, home office studies, social isolation, and previous HCI related papers connected with the overall theme of the research questions and the methodologies used in our research. Four papers have been identified as either approaching the notion of distance learning motivation and competencies \cite{kolodziejczak_roszak_2017, simons_leverett_beaumont_2019}, students' preferred learning environments \cite{beckers_voordt_dewulf_2016}, or other works related to the impact that office comfort has on productivity \cite{sakellaris_et_al._2016}.

Using \emph{Google Scholar} and the search inputs containing \emph{distance learning}, \emph{pandemic}, \emph{study environment}, \emph{COVID-19}, close to none have been found on the specific topic of the 2020 pandemic influences on distance learning, likely due to it being the first ever moment in human history that an epidemiological issue of this proportion has been encountered in the age of the internet, allowing the possibility of partaking in educational activities without putting one's life at risk. In the most relevant paper found, Lovric et al\cite{Lovri__2020}, the researchers performed an analysis on nursing students' perception of their overall experiences while studying during the COVID-19 pandemic, highlighting students' increasing worries and preference that educational institutions extend the already ongoing distance learning procedures.

Upon reviewing different research methodologies and scientific papers through the course \emph{193.055 User Research Methods}, the authors have decided to proceed with a research strategy involving auto-ethnography, semi-structured interviews, and photographic ethnography\cite{adams_ellis_jones_2017, adams_2015, douglas_2003, schwartz_visual_1989} considering these methodologies as being the most appropriate, and capable of creating a coherent strategy for the short amount of time and resources available.

@@

The following section will describe the research question, as well as the methods used in the research study, to show how these methods are integrated with each other in order to create a research strategy.

\subsection{Research Questions}

A distinct but primitive research question was designed to guide the research. The fundamental idea of the research question was to \textit{investigate how the home environment of the university student has changed to accommodate full-time study under the restrictions of the COVID-19 pandemic}. In order to answer this main research question, it was broken down into two more concrete secondary research questions, which would explore \textit{how the location of the study area has changed}, as well as \textit{how the equipment of the study area has changed}.

\subsection{Methodologies}
In order to perform the research as best as possible, we decided on utilizing three separate methodologies in order to achieve a coherent approach and take into account various aspects related to the \emph{study environment}. We started by performing auto-ethnography upon ourselves to have an introspective look over our own experience during the first and second semesters of our studies within the context of the pandemic restrictions. Using the findings of the auto-ethnography, we arrived at a number of interview questions that where used in a series of semi-structured interviews with participants outside of the research team. Lastly by performing a photographic ethnography of the pictures taken by the same interview participants in order to analyse them in parallel with the interview transcriptions, a more coherent image of each participants' actual study environments is achieved. The following sections will explain which methods are used and our overall methodological strategy.

@@

The research began with the auto-ethnography \cite{adams_ellis_jones_2017, dighe_joshi_2014} approach. Each researcher conducted an inner-inquiry upon their experience that resulted from the drastic change to full-time distance learning, as well as making a comparison between their study/work environment and their study workload between previous semesters.

Upon finishing our reports on our own experience, each researcher had to take a photograph of their current study environment (see Figure~\ref{fig:figure1} as an example) and attach it to their report. Afterwards all reports where analysed by each researcher and the researcher-participant had to present their experience to the team. The information was then analysed using \emph{thematic analysis} within \emph{Miro}\footnote{\url{https://miro.com}} so as to extract possible interview questions for later use. After having decided on the possible interview questions, a practice semi-structured interview took place, with one of the researchers as a participant, and two others as interviewer and observer. Upon finishing the sample interview, the interview questions were refined down to five central questions that were used as a guide for the participant interviews.
\begin{figure}
\centering
  \includegraphics[width=1\columnwidth]{figures/auto-ethnography.JPG}
  \caption{Sample photograph from the auto-ethnographic method, showing the desk of one of the researchers}~\label{fig:figure1}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\columnwidth]{figures/auto-ethnography-annotated.JPG}
  \caption{Applying annotation to the same photograph as shown in Figure \ref{fig:figure1}}~\label{fig:figure2}
\end{figure}

\subsubsection{Semi-structured Interviews}
Semi-structured interviews\cite{adams_2015} were conducted to gather more information on how the home studying environment had changed for a variety of students. We opted for this more open style of information gathering because of the diverse variety of possible living situations.

Our participants were friends and colleagues from varying backgrounds, countries, universities, and degree programs. An overview of their basic information is shown in Table \ref{tab:table1}. Using our interview questions as a guide to prompt a discussion on a specific point of interest, the semi-structured format allowed us to ask follow-up questions to further explore the participants' unique situations. These details may not have been captured in a more strictly structured interview or by a survey.

The topics that guided our interview questions centered on the home and study-area environment. First we asked questions to determine their current student and work status in order to get an idea for how heavy their work-loads were. This helped us understand how intensely they use their home office, and how important it is for their work and studies. We also asked questions about their living situations to understand how they might deal with issues of privacy, noise or other distractions, and sharing study-spaces with cohabitants. We then asked about their study-area and immediate surroundings. This gave us a picture of their immediate study environment; what equipment they use and how they use the space. We also asked them to think about the semester before the pandemic, and to reflect upon any changes they made to their study areas since transitioning to full-time distance learning. This includes rearranging furniture, purchasing or upgrading new equipment, or using old things in new ways. We then asked about any issues or challenges present in their current studying environment. Finally we asked them to imagine their ideal study area, and to share any improvements or "wish-list" items they would like if they could change anything and afford to do so. 
\begin{table}
  \centering
  \begin{tabular}{l l l l}
    % \toprule
    & & \multicolumn{2}{c}{\small} \\
    \cmidrule(r){1-4}
    {\small\textit{ID}}
    & {\small \textit{Academic Program}}
      & {\small \textit{Living Space}}
    & {\small \textit{Study Space}} \\
    \midrule
    P1 & Bio-Med Engineering & Shared Apt. & Bedroom \\
    P2 & Interaction Design & On-Campus & Shared Dorm \\
    P3 & Mechatronics & On-Campus & Shared Dorm \\
    P4 & Physics & Shared Apt. & Bedroom \\
    P5 & Data Science & Shared Apt. & Bedroom \\
    P6 & PhD Law & Apartment & Living-room \\
    P7 & Data Science & With Parents & Bedroom \\
    P8 & Artificial Intelligence & With Parents & Bedroom \\
    % \bottomrule
  \end{tabular}
  \caption{A variety of living and studying situations}~\label{tab:table1}
\end{table}

The participants were invited to take part in a short interview of approximately 30 minutes to discuss their current home studying environment, and to compare it with a semester before the pandemic. They were given information sheets and consent forms, informing them that their identities would remain anonymous to all but the interviewer and the consent form manager. They were also asked to provide a photograph of their studying area for photographic ethnography.

To avoid risk of COVID-19 exposure to both participant and researcher, all interviews were conducted via video conferencing and recorded with consent from the participant. The researcher then transcribed the recordings using \emph{Temi}\footnote{\url{https://www.temi.com}}. The transcriptions were finally anonymized and shared with the team for analysis. We then applied thematic analysis to the content of the transcripts on a shared Miro board. The themes and patterns that emerged are discussed in the Findings section.

\subsubsection{Photographic Ethnography}
Using the photographic ethnography method, we attempted to study the home study spaces of participants in more detail. The method was chosen in order to give a better overview of essential items used by students for improving their health and comfort during online studies at home. The participants agreed on sending a photograph of their study environment before the semi-structured online interviews in a email to the researcher who provided the consent forms. Moreover, the photographs of the researchers' personal setups, provided in the auto-ethnography phase, were also analyzed. The processes of storing, analyzing, anonymizing, and deleting the participants' and researchers' photographs were covered in the consent forms signed for the semi-structured online interviews and for auto-ethnography.

As visual recording of one's personal space can be considered a breach of privacy. Not all the participants agreed to photograph their study areas. In all, 21 photographs were collected in the photograph ethnography process. Some participants sent multiple photographs of their desk from different perspectives. A visual comparison between the state of the learning environment before and after switching to distance learning could not be made, as the photographs received were taken in the current context of the pandemic. One participant sent a photograph of their current setup, and two pictures of their ideal study space that could serve as inspiration for their future office arrangement (see Figure~\ref{fig:figure3}\cite{instagram_2019}). All photographs received by the participants were used in the analysis process.

The photographic ethnography method was used as an independent method to make a classification of the items used by students in the distance learning process, but also as a complementary method for the semi-structured interviews, to help us in having a more clear visualization of the environments of the participants. After collecting and anonymizing all the visual data, we arranged the photographs in Miro by a color and number code scheme. Every photograph would have the same number and color as the interview notes, which made sure we analyzed the transcripts of the corresponding photographs. This method of classification was used to offer a better correlation between the described environment and the representative photograph.

For an easier understanding of one's home study area, the photographs sent by us were completed with short annotations on objects present in the image (see Figure \ref{fig:figure2}). Each note summarized what the specific object is, what it is used for, and how it improves the quality or efficiency of the distance learning process.

\begin{figure}
\centering
  \includegraphics[width=1\columnwidth]{figures/perfect-setup}
  \caption{A sample picture from the Photographic Ethnography method given by one of the participants; it shows the desired \emph{perfect study environment}}~\label{fig:figure3}
\end{figure}

@@

\subsection{Auto-ethnography}
Every researcher that took part in the auto-ethnographic process is currently taking part in distance learning, differing in degree program and the number of credits per semester. Some researchers admitted to registering for more courses this semester than in a typical, on-campus semester. The rationale was that commuting to the university is no longer required, and activities outside the house are restricted by the current regulations, which frees up more time for coursework. One participant admits that they overestimated the extra time that could be gained from not commuting, traveling, or taking part in social activities. Every researcher had to implement changes in their everyday schedule and their way of working on group projects or individual assignments, in order to respect the regulations in place caused by the pandemic:

\begin{quote}
\emph{All the projects I was doing at home, inviting colleagues over, at their place or in a coffee place. Now all the meetings are remote.}
\end{quote}

All researchers made changes to their home study setup. One participant who received an ergonomic desk and an additional monitor from their employer focused more on improving the room aesthetics, decorating with plants and drawings, and painting their wall. They mentioned that creating a comfortable, cozy place improves efficiency during working time. Another participant changed the location of their study area from a common room to a guest room that is no longer being used due to the restrictions. This change in location was to avoid being disturbed in the common room.

All researchers want to improve their current study area as the distance learning may extend into the future. Common items that are desired for creating a more effective study space are ergonomic chairs, adjustable height desks, better headsets, second monitors, desk lamps, or even separate working/studying places at home.

\subsection{Semi-structured Interviews}
After transcribing the recorded interviews, we read each-others' transcripts and analysed them. Using thematic analysis we identified some emerging themes. The most common themes were disruptions and annoyances in the home, complaints about poor ergonomics that resulted in pain, the importance of lighting, and strategies to maintain focus and motivation.

We found that all but one student made changes or improvements to their home study environment. This student still attends lectures on-campus, but at reduced capacity. The frequency with which they study at home has not notably increased since the pandemic. Equipment upgrades included purchasing a printer and scanner, improving lighting, new headsets or noise-cancelling headphones, a laptop stand, a power strip, new house plants, and lumbar support to prevent back pain. Some changes that did not require spending any money include moving furniture to create a more separate dedicated study area, moving desks closer to a window for better lighting, and using a whiteboard that went previously unused.

We found that even if sharing a home with other people, most participants now have a dedicated study area where they can be alone, where before they had to share their study space with others or study in a common area. The exception are the students who live on-campus in a dormitory.

In most cases the desk and study area is in the bedroom. This combination of study and sleeping space was sometimes a problem for some participants. One participant said it was difficult to take breaks and relax because they were surrounded by reminders of work, where when they were attending lectures on-campus there was enough of a separation to make the switch mentally. Some students combat this by making a point to do all school-related work only at the desk, where before they might have done some studying on the couch, in a chair, or in bed.

Some people were initially reluctant to make changes or invest money because of the uncertainty about how long the pandemic restrictions will remain in effect. At the time of this writing, we are currently in our second distance learning semester. While most of the changes discussed by our participants were enacted in their first pandemic semester, some larger purchases finally were made during the second pandemic semester.

Lastly we asked how their ideal setup would look like if they could make further changes or investments. The most common ``wish-list'' item was a more comfortable chair. Students are spending sometimes over 12 hours in their chairs. Reports of back pain were the most common complaint among our interviewees.

\subsection{Photographic Ethnography}
We analyzed 11 sets of photographs both from the participants involved in the interview and from ourselves. We found that every student has a dedicated study setup place at home, arranged to meet the everyday needs for distance learning in the current situation of the pandemic. Every setup has a dedicated study desk, a chair, a laptop and ornamental items arranged on or around the desk. The ornaments were personal photos, trophies, flags, drawings or Christmas decorations. We classified those items that are present in every setup as “indispensable items”. Other relevant items, that were present in most of the study environments of our participants were lamps or any other source of artificial lighting, decorative plants on or near the desk, storage boxes or drawers containing books or other learning related supplies, second screens, pencils and paper used for writings, and headphones or speakers. We observed that the participants who do not have a good ergonomic chair use pillows to support the back while sitting. One of the photographs shows a setup with a chair and a professional lumbar support. We categorized those items as “items present in most of the study environments”. Items that were present only in one or two of the analyzed study spaces consisted of additional equipment that can improve productivity, such as an iPad or a scanner, but mostly related to the students' hobbies or particular academic area of interest: Raspberry Pi board connected to diverse sensors, gaming console, electronics used for personal projects, or painting brushes. Another finding consists in a small number of participants who use two laptops. This can be used to separate academic studies from work related activities. For example, one participant used one laptop for notes and the other for work, or to record one lecture for later watching while simultaneously attending another.

One participant submitted two photographs of their ideal home study environment, that they may use as inspiration. Large desks with an artificial sources of light are presented. One setup is focusing more on technical equipment as it pictures a desktop for gaming, three monitors, and different controllers for a Nintendo console. The rooms are decorated in different styles; one with comics, books, portraits of fictional characters and figurines, and another in a more simple aesthetic focusing on objects like books, electronics like a Raspberry Pi board, small plants, inspiring framed quotes on the wall, and a warm blanket on the chair (See Figure 3).

@@

The following section will discuss the findings achieved and analyze them from different perspectives. Each subheading explains the type of perspective being discussed.

\subsection{Biases in Participation}
%Not used
\begin{comment}
There was an obvious variation in the results we achieved. It is therefore feasible to discuss what the research results would have looked like if the number of participants had been higher, or if the participants had studied other educational disciplines. Most of the participants were students at the Vienna University of Technology in Austria, which is a delimitation. Overall, We felt that the wide variety of situations among these students would help us identify many different types of problems and solutions.
\end{comment}

Upon closer look within the participants' characteristics, it must be noted that our “sample” is not very diverse from a geographical point of view. All participants, including ourselves, live and study either in Austria or another EU member country. In terms of education level, only Bachelors, Masters, and PhD students have participated, no lower education. The degrees have been mostly IT or science related, from Vienna University of Technology or other European universities, as well as Erasmus students in Vienna.

An important bias that had occurred within our interviews is due to the already existing relationships between us and the interview participants, as well as the decision of not utilizing the classical interviewer and observer technique due to time constraints as well as to avoid causing discomfort towards the participants in discussing their lives with an unknown person in the interview. It is also possible to consider in what way our prejudices have affected the results achieved. This remains uncertain but can be observed by discussing the results objectively.

One of the participants in the study also participated in a hybrid semester, which differs from the other participants' situations. A hybrid semester means that the practical laboratories take place at the university on-site, while still following social distance measures. The participant mentioned that the mixture of having access to the university's resources, having regular social interaction but also maintaining the flexibility and benefits of studying from home during certain weekdays, is a perfect balance between academic and private life. We therefore want to emphasize the strength of being able to carry out studies with a hybrid solution. The student can then carry out pandemic-safe studies even if parts of the curriculum take place on campus, precisely because the campus is not fully occupied.

\subsection{Motivation}
While the discussion topics focused mainly on the physical space, equipment, and devices used by the students to facilitate effective learning, some students mentioned that the new restrictions have challenged their motivation and mental health. Some of the coping strategies shared by our interviewees include moving the desk closer to a window to increase natural lighting and allow them to look outside, setting houseplants around their work-space, distinguishing between work and relaxation time by doing school related work strictly at the desk, and connecting with friends or colleagues on a video chat left on in the background for the effect of having company.
